CDSR Human Data/Modelling Paper

### 2013-09-11 code/scenarios/cdsr/trunk/papers/ACS2013/main.tex
JK added a discussion of the P2 ratings into the paper

Table \ref{tab:point-likert-scores} lists the average likert scores for the different points in each domain. For each stimuli we have highlighted in bold the maximum average likert rating for a point for that stimuli. In all cases the expected sweetspot received the maximum average likert rating for trials using that stimuli. For each stimuli we tested whether the higher ratings of the sweetspot locations was statistically significant using one-tailed two sampl t-tests. There were two of these t-tests carried out for each stimuli, each one tested whether the sweetspot ranking was statistically higher than one of the other points. Table \ref{tab:point-likert-scores} also lists the results of these t-tests for each stimuli. In all cases, the results indicate that the null hypothesis, $H_0$, should be rejected and that the alternative hypothesis, namely that the sweetspot was rated significantly higher than the other point, could be accepted with $\alpha=0.05$.

As noted above, we controlled for left-right bias by flipping some of the stimuli on the horizontal axis. These flipped stimuli included the classroom stimuli (c), (e) and (f). This flipping of stimuli gave us the opportunity to compare the results of the sweetspots rankings between this pairs of stimuli trials. Given the horizontal flipping of the stimuli it was expected that the sweetspot for the stimuli should also be flipped between P1 and P3. To test whether or not the expected shift in the sweetspots occurred we ran two-tailed two sample t-tests between the sweetspots of the flipped and non-flipped stimuli pairs. Table \ref{tab:flipped-point-likert-scores} lists the results of this trial. In all cases the results indicated that there was not enough evidence to reject the null hypothesis, in other words there was no statistical difference between the rating of the sweetspot for the non-flipped stimuli and the rating of the sweetspot for the flipped stimuli.

\begin{figure}
%\includegraphics[width=0.4\textwidth]{figures/turrets-plus-one.jpeg}
\centerline{
\begin{tabular}{ccc}
\begin{subfigure}[b]{0.3\textwidth}\includegraphics[width=\textwidth]{figures/classroom-circle-points.png}\caption{}\label{fig:classroom-points}\end{subfigure}&
\begin{subfigure}[b]{0.3\textwidth}\includegraphics[width=\textwidth]{figures/bottleneck-2-points.png}\caption{}\label{fig:bottleneck-points}\end{subfigure}&
\begin{subfigure}[b]{0.3\textwidth}\includegraphics[width=\textwidth]{figures/tanks-close-points.png}\caption{}\label{fig:tanks-points}\end{subfigure}\\
\end{tabular}
}
\caption{The pre-selected locations for each domain used in the Type 2 Trials.}
\label{fig:locations}
\end{figure}

>>>>

Table \ref{tab:point-likert-scores} lists the average likert scores for the different points in each domain. For each stimuli we have highlighted in bold the maximum average likert rating for a point for that stimuli. In all cases the expected sweetspot received the maximum average likert rating for trials using that stimuli. For each stimuli we tested whether the higher ratings of the sweetspot locations was statistically significant using one-tailed two sample t-tests and in all cases the ranking of the sweetspot was found to be significantly higher than either of the other two points using a confidence level of $95\%$. 
%There were two of these t-tests carried out for each stimuli, each one tested whether the sweetspot ranking was statistically higher than one of the other points. Table \ref{tab:point-likert-scores} also lists the results of these t-tests for each stimuli. In all cases, the results indicate that the null hypothesis, $H_0$, should be rejected and that the alternative hypothesis, namely that the sweetspot was rated significantly higher than the other point, could be accepted with $\alpha=0.05$.

As noted above, we controlled for left-right bias by flipping some of the stimuli on the horizontal axis. These flipped stimuli included the classroom stimuli (c), (e) and (f). This flipping of stimuli gave us the opportunity to compare the results of the sweetspots rankings between this pairs of stimuli trials. Given the horizontal flipping of the stimuli it was expected that the sweetspot for the stimuli should also be flipped between P1 and P3. To test whether or not the expected shift in the sweetspots occurred we ran two-tailed two sample t-tests between the sweetspots of the flipped and non-flipped stimuli pairs. In all cases the results indicated that there was no statistical difference between the rating of the sweetspot for the non-flipped stimuli and the rating of the sweetspot for the flipped stimuli using a confidence level of $95\%$. In other words, the sweetspot flipped from P1 to P3 systematically with the horizontal flipping of the stimuli. Another way of testing the relationship between the variation in context and the variation in definition of the CDSRs is to look at the differences in the ranking of the P2 point in the miliatary engagement domain between the pair of stimuli (i) and (j) and the pair of stimuli (k) and (l). In stimuli (i) the friendly tanks are positioned between the P2 point and the enemy tanks whereas in stimuli (j) the P2 point is in no-mans land. Given this change in the context one would expect a higher ranking for the P2 point in context (i) than in context (j). As the results in Table \ref{tab:point-likert-scores} show this is the case with average rating of P2  stimuli (i) being higher than that for (j). This higher rating is statiscially significant at a $95\%$ confidence level. Stimuli (k) and (l) present and analagous situation with P2 being protected by an extra turret in stimuli (l) but in no-mans land in stimuli (k). Again, the average rating of P2 for stimuli (l) is higher than that of (k), although this difference is not statistically significant. Notice, that the rating of the sweetspot for the stimuli (i) and (l) remain quite high. This would indicate that the increase in the rating of the P2 points for these stimuli results from an increase in the area of the CDSR rather than a moving of the locus of the CDSR. Overall, the analysis of the ratings of the different sweetspots across the non-flipped and flipped stimuli and the variation in the ratings of the P2 points in the military domain stimuli point to the fact that both the location and the extent of a CDSR is contextually dependent.

%\begin{figure}
%%\includegraphics[width=0.4\textwidth]{figures/turrets-plus-one.jpeg}
%\centerline{
%\begin{tabular}{ccc}
%\begin{subfigure}[b]{0.3\textwidth}\includegraphics[width=\textwidth]{figures/classroom-circle-points.png}\caption{}\label{fig:classroom-points}\end{subfigure}&
%\begin{subfigure}[b]{0.3\textwidth}\includegraphics[width=\textwidth]{figures/bottleneck-2-points.png}\caption{}\label{fig:bottleneck-points}\end{subfigure}&
%\begin{subfigure}[b]{0.3\textwidth}\includegraphics[width=\textwidth]{figures/tanks-close-points.png}\caption{}\label{fig:tanks-points}\end{subfigure}\\
%\end{tabular}
%}
%\caption{The pre-selected locations for each domain used in the Type 2 Trials.}
%\label{fig:locations}
%\end{figure}
